The Second Data Release of the INT Photometric H$\alpha$ Survey of the Northern Galactic Plane (IPHAS DR2)

### 2014-03-12 paper/iphas-dr2.tex
removing strange duplication of tex

\end{document}\documentclass[useAMS,usenatbib]{mn2e}
\usepackage{amssymb,amsmath}
\usepackage[pdftex]{graphicx}
\usepackage{longtable} 
%\usepackage{lscape}
\usepackage{float}
\usepackage{booktabs}
\usepackage{aas_macros}

Each of the sightlines reveals a stellar population
with distinct characteristics.
Firstly, towards the Galactic anti-centre at $l=180^\circ$ (Fig.~\ref{fig:l180}) 
we find a population dominated by lowly-reddened 
main sequence stars and an apparent absence of reddened giants.
%consistent with the sightline extinction of XX from Schlegel (cite). 
In contrast, closer towards the galactic
centre at $l=45^\circ$ (Fig.~\ref{fig:l45})
we find a wealth of reddened objects
which appear to be separated into a lowly
and a highly reddened component,
perhaps revealing two distinct parts of the Galaxy.
Finally, in one of our earliest sightlines at $l=30^\circ$
we find a very high number of extremely reddened giants
in addition to an unreddened population
of foreground dwarfs.

The number density of stars in the colour-colour
and colour-magnitude space
can be compared against population synthesis models
to create three-dimensional maps of the extinction
across several kpc \citep{Sale2010,Sale2012}.
Such an extinction map based on our catalogue
is to be released in a separate paper
that accompanies this data release (Sale et al., in preparation).

\begin{figure*}
    \begin{minipage}[b]{\linewidth}
        \includegraphics[width=0.5\textwidth]{./plots/ccd-180-3.pdf} 
        \includegraphics[width=0.5\textwidth]{./plots/cmd-180-3.pdf}
    \end{minipage}
    \caption{Colour-colour and colour-magnitude diagram (left and right panel)
    showing sources flagged as \emph{veryReliable}
    located in an area of one square degree
    centred near the Galactic anti-centre 
    at $(l,b)=(180^\circ,+3^\circ)$.
    The colour-colour diagram shows the
    position of the main sequence (thin solid line),
    giant stars (thick solid line)
    and the reddening track for an A0V-type star (dashed line)
    based on the \citet{Pickles1998} library of empirical spectra.
    The colour-magnitude only show the reddening vector
    along with the unreddened 1~Gyr isochrone due to \citet{Bressan2012},
    which has been placed at an arbitrary distance of 2~kpc for reference.
    This is one of the least reddened sightlines
    in the survey %(Av XX, Schlegel et al. XXXX)
    and hence the observed stellar population appears to be dominated 
    by lowly reddened main sequence stars.}
    \label{fig:l180}
    \begin{minipage}[b]{\linewidth}
        \includegraphics[width=0.5\textwidth]{./plots/ccd-45-2.pdf}
        \includegraphics[width=0.5\textwidth]{./plots/cmd-45-2.pdf}
    \end{minipage}
    \caption{Same as above for $(l,b)=(45^\circ,+2^\circ)$,
    which is one of the highest-density sightlines in the survey,
    revealing a population of stars with a reddening distribution
    that appears to be bi-model.}
    \label{fig:l45}
    \begin{minipage}[b]{\linewidth}
        \includegraphics[width=0.5\textwidth]{./plots/ccd-30-0.pdf}
        \includegraphics[width=0.5\textwidth]{./plots/cmd-30-0.pdf} 
    \end{minipage}
    \caption{Same as above for $(l,b)=(30^\circ,0^\circ)$.
    This is one of the most reddened sightlines in the survey.
    %(XXX, Schlegel et al XXXX).
    }
    \label{fig:l30}
\end{figure*}

\end{document}

>>>>

\end{document}\documentclass[useAMS,usenatbib]{mn2e}
